Hierarchical Dispatching and Overriding

### 2017-09-30 NewVersion/sections/Formalization.tex

@@

\begin{figure*}
\saveSpaceFig
\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\
	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	% \tsuperinvk \\
	% \tstaticinvk  \\
	\tnew \\
	\tmethod \\
	\tabsmethod \\
	\tintf \\
	\tanno
\end{mathpar}
\label{fig:typingrules}
\saveSpaceFig
\caption{Typing and subtyping of \name{}.}
\end{figure*}

>>>>

There are two typing rules for method invocation: \textsc{(T-Invk)} and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement for a normal method invocation, which is similar to Featherweight Java. It checks the type of the specific method, by using an auxiliary function \mbody. \mbody is the function for looking up methods, which we will illustrate later in Section~\ref{subsec:auxdefs}. After the method type is obtained, we check that arguments and the receiver have compatible types. \textsc{(T-PathInvk)} is the typing judgement for a path invocation. Besides the conditions of \textsc{(T-PathInvk)}, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
path type. 
% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

\textsc{(T-New)} is the typing rule for object creation $\new{I}$. The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not. If interface $I$ contains (or inherits) any abstract method that has not been implemented, then interface $I$ cannot be instantiated.

@@

\begin{figure*}
\saveSpaceFig
\begin{mathpar}
	\framebox{$ I <: J $} \hspace{.5in} \subid \\
	\subtrans \hspace{.5in} \subextends \\

	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	% \tsuperinvk \\
	% \tstaticinvk  \\
	\tnew \\
	\tmethod \\
	\tabsmethod \\
	\tintf \\
	\tanno
\end{mathpar}
\caption{Typing Rules of \name{}.}
\label{fig:typingrules}
\saveSpaceFig
\caption{Typing and subtyping of \name{}.}
\end{figure*}
